Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-05-18 Manuscript/proto-manuscript.tex

- Figure comparing order parameters (Fig.~\ref{HGopsNEWmodels}) and form factor \todoii{Add plot}{Add the form factor plot} between original Lipid14, new model and experiments,

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{fig:form-f}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.}
\end{figure}

@@

>>>>

- Figure comparing order parameters (Fig.~\ref{HGopsNEWmodels}) and form factor \todoi{The original L14 form-f are worse than those in the L14 paper -- I'd better double check it and make sure I use the same settings and version for all simulations consistently for a good comparison.}between original Lipid14, new model and experiments,

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{fig:form-f}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 and ECCLipids17 models.  }
\end{figure}

@@

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm,angle=0]{../Fig/CAdensities.eps}
  \caption{\label{fig:cacl-dens}
    Density profiles of \ce{Ca^{2+}} and \ce{Cl^-} for Lipid14 model with Aquist parameters and with ECC ions and ECCLipids17 with ECC ions. }
\end{figure}
